Figures

### 2016-01-19 scripts/figures.Rmd
starting to put boxes together

Here are the figures (or figure panels) we are thinking of using in the Benchmarking paper.  I will include my comments and decriptions on each and perhaps over time this will develop into the results section
```{r,settings_and_lib,echo=F,message=F,}
require(ggplot2)
require("plyr")
require("Biostrings")
require(reshape2)
require("pROC")
require(gridExtra)
theme_set(new = theme_classic(base_size=24))
require(knitr)
opts_chunk$set(fig.align = "center", warning = FALSE, echo = FALSE, fig.width = 10, 
    fig.height = 7,message=F)
```

@@

 #plot the points and cut offs
 points.p<-ggplot(distribution,aes(x=1,y=test,fill=Condition))+geom_dotplot(binaxis = "y", stackdir = "center")+scale_fill_manual(values=c("white","black"),name="",breaks=c(T,F),labels=c("True Positive","False Positive"))+xlab("")+ylab("Log(p value)")+theme(axis.ticks = element_blank(), axis.text.x = element_blank(),axis.title.y = element_text(vjust=1.2))

@@

 grid.arrange(points.p,roc.p,ncol=2)

}
plot.ex(0.35,0.95,roc.df,example)
pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/roc.ex.pdf")
plot.ex(0.35,0.95,roc.df,example)
dev.off()

@@

miseq.roc.p<-ggplot(m.roc.df,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

Hiseq.roc<-ggplot(subset(h.roc.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005));Hiseq.roc

@@

Hiseq.roc.4<-ggplot(subset(h.roc.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005));Hiseq.roc

@@

mapq_phred.roc<-ggplot(subset(h.cut.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

read.roc<-ggplot(subset(h.cut.read.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

## Figure 5 Lower inputs
### 10^4
```{r,roc_lower_inputs4}
roc.4<-ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

### 10^3
```{r,roc_lower_inputs3}
roc.3<-ggplot(subset(h.cut.read.df,gc==3),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

dups.roc.p<-ggplot(dups.roc,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

>>>>

Here are the figures (or figure panels) we are thinking of using in the Benchmarking paper.  I will include my comments and decriptions on each and perhaps over time this will develop into the results section
```{r,settings_and_lib,echo=F,message=F,}
require(ggplot2)
require("plyr")
require("Biostrings")
require(reshape2)
require("pROC")
require(gridExtra)
theme_set(new = theme_classic())
require(knitr)
opts_chunk$set(fig.align = "center", warning = FALSE, echo = FALSE, fig.width = 10, 
    fig.height = 7,message=F)
```

@@

 #plot the points and cut offs
 points.p<-ggplot(distribution,aes(x=1,y=test,fill=Condition))+geom_dotplot(binaxis = "y", stackdir = "center")+scale_fill_manual(values=c("white","black"),name="",breaks=c(T,F),labels=c("True Positive","False Positive"))+xlab("")+ylab("Log(p value)")+theme(axis.ticks = element_blank(), axis.text.x = element_blank(),axis.title.y = element_text(vjust=1.2))+xlab("")

@@

 plot_grid(points.p, roc.p, labels=c("A", "B"), ncol = 2, nrow = 1)

}
plot.ex(0.35,0.95,roc.df,example)
# pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/roc.ex.pdf",width = 12,height = 8)
# plot.ex(0.35,0.95,roc.df,example)
# dev.off()

@@

miseq.roc.p<-ggplot(m.roc.df,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))

@@

Hiseq.roc<-ggplot(subset(h.roc.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5));Hiseq.roc

@@

Hiseq.roc.4<-ggplot(subset(h.roc.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005));Hiseq.roc.4

@@

mapq_phred.roc<-ggplot(subset(h.cut.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))

@@

read.roc<-ggplot(subset(h.cut.read.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))

@@

## Figure 5 Lower inputs
### 10^4
```{r,roc_lower_inputs4}
roc.4<-ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))

@@

### 10^3
```{r,roc_lower_inputs3}
roc.3<-ggplot(subset(h.cut.read.df,gc==3),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

dups.roc.p<-ggplot(dups.roc,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))
